jk test with unbalanced label

### 2016-10-19 Rmd/convergenceRatesBalancedBigK.Rmd
rerun tests after fixing initialization

```{r}
n<- 100
K<- 10
p<- 1
batchN<- 1000

@@

  yBatch<- array(0,dim = c(n*K,p,batchN))
  K<- 10

@@

  jk12 <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T)
  jk22 <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = K,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T)
  jGMM12 <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F)
  jGMM22 <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = K,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F)

  error <- cbind( computeMError(jk12,n, batchN), computeMError(jk22,n,batchN), computeMError(jGMM12,n,batchN),computeMError(jGMM22,n,batchN))
  rmse <- cbind( computeRMSE(jk12,mu0,batchN), computeRMSE(jk22,mu0,batchN), computeRMSE(jGMM12,mu0,batchN),computeRMSE(jGMM22,mu0,batchN))

@@

  save(result, file="resultRatesBigK3.Rda")
}

@@

load("resultRatesBigK3.Rda")

plot1<- data.frame( "n" = rep(nSeries, 4),
            "MC14Error"= c(result$MCEmean),
            "MC14ErrorL"= c(result$MCEq25),
            "MC14ErrorU"= c(result$MCEq975),
            "Model"= rep(c("K-Means","W-constraint-GMM (22-Means)","1-sparse-GMM","GMM"),each= length(nSeries))
            )

@@

# p+ geom_errorbar( aes(x=n,ymax = MC14ErrorU, ymin=MC14ErrorL, colour=Model),width=0.2)
p+ theme_bw()
pE + theme_bw()
```

@@

plot1<- data.frame( "n" = rep(nSeries, 4),
            "RMSE"= c(result$RMSEmean),
            "RMSEL"= c(result$RMSEq25),
            "RMSEU"= c(result$RMSEq975),
            "Model"= rep(c("K-Means","W-constraint-GMM (22-Means)","1-sparse-GMM","GMM"),each= length(nSeries))
            )

@@

p+ theme_bw()
pE + theme_bw()
```

>>>>

```{r}
n<- 100
K<- 5
p<- 1
batchN<- 1000

@@

  mu0<- c(1:K)
  mu<- matrix( 0,n*K,p)
  mu <- rep(mu0, each = n)

@@

  jk1 <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T,sigma2_ini = sigma^2)
  jk2 <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = 2,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T,sigma2_ini = sigma^2)
  jk3 <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = 3,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T,sigma2_ini = sigma^2)
  jk4 <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = 4,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T,sigma2_ini = sigma^2)
  jkK <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = K,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T,sigma2_ini = sigma^2)

  jGMM1 <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F,sigma2_ini = sigma^2)
  jGMM2 <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = 2,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F,sigma2_ini = sigma^3)
  jGMM3 <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = 3,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F,sigma2_ini = sigma^2)
  jGMM4 <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = 4,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F,sigma2_ini = sigma^2)
  jGMMK <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = K,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F,sigma2_ini = sigma^2)

  runRes <- list(jk1,jk2,jk3,jk4,jkK, jGMM1, jGMM2, jGMM3, jGMM4, jGMMK)

  error<- sapply(runRes,function(x){computeMError(x,n,batchN)})
  rmse<- sapply(runRes,function(x){computeRMSE(x,mu0,batchN)})

@@

  save(result, file="resultRatesBigK.Rda")
}

@@

```{r echo=FALSE}

load("resultRatesBigK.Rda")

plot1<- data.frame( "n" = rep(nSeries, 5),
                    "MC14Error"= c(result$MCEmean[,1:5]),
                    "MC14ErrorL"= c(result$MCEq25[,1:5]),
                    "MC14ErrorU"= c(result$MCEq975[,1:5]),
                    "Model"= rep(c("w fixed, J=1","w fixed, J=2","w fixed, J=3","w fixed, J=4","w fixed, J=K"
                    ),each= length(nSeries))
)

@@

# p+ geom_errorbar( aes(x=n,ymax = MC14ErrorU, ymin=MC14ErrorL, colour=Model),width=0.2)
p+ theme_bw()
# pE + theme_bw()
```

```{r echo=FALSE}

plot1<- data.frame( "n" = rep(nSeries, 5),
                    "MC14Error"= c(result$MCEmean[,6:10]),
                    "MC14ErrorL"= c(result$MCEq25[,6:10]),
                    "MC14ErrorU"= c(result$MCEq975[,6:10]),
                    "Model"= rep(c("w flex, J=1","w flex, J=2","w flex, J=3","w flex, J=4","w flex, J=K"
                    ),each= length(nSeries))
)

# p+ geom_errorbar( aes(x=n,ymax = MC14ErrorU, ymin=MC14ErrorL, colour=Model),width=0.2)
p+ theme_bw()
# pE + theme_bw()
```

@@

```{r echo=FALSE}

plot1<- data.frame( "n" = rep(nSeries, 5),
                    "RMSE"= c(result$RMSEmean[,1:5]),
                    "RMSEL"= c(result$RMSEq25[,1:5]),
                    "RMSEU"= c(result$RMSEq975[,1:5]),
                    "Model"= rep(c("w fixed, J=1","w fixed, J=2","w fixed, J=3","w fixed, J=4","w fixed, J=K"

                    ),each= length(nSeries))            )

@@

p+ theme_bw()
# pE + theme_bw()
```

```{r echo=FALSE}

plot1<- data.frame( "n" = rep(nSeries, 5),
                    "RMSE"= c(result$RMSEmean[,6:10]),
                    "RMSEL"= c(result$RMSEq25[,6:10]),
                    "RMSEU"= c(result$RMSEq975[,6:10]),
                    "Model"= rep(c(
                                   "w flex, J=1","w flex, J=2","w flex, J=3","w flex, J=4","w flex, J=K"
                    ),each= length(nSeries))            )

p+ theme_bw()
# pE + theme_bw()
```

### 2016-10-19 Rmd/convergenceRatesImbalanced.Rmd
rerun tests after fixing initialization

  jk12 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T)
  jk22 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 2,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T)
  jGMM12 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F)
  jGMM22 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 2,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F)

  jGMMFlex <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F,flexJ = T,zetaTrunc = 0.05)

>>>>

  jk12 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T,sigma2_ini = sigma^2)
  jk22 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 2,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T,sigma2_ini = sigma^2)
  jGMM12 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F,sigma2_ini = sigma^2)
  jGMM22 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 2,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F,sigma2_ini = sigma^2)

  jGMMFlex <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F,flexJ = T,zetaTrunc = 0.05,sigma2_ini = sigma^2)
